### 2015-01-28 doc/tutorial/introduction.Rmd
make predictions option

>>>>

## Speed

It is possible to bypass any extra-I/O and directly communicate with the SVM Package by specifying the training and test data as well as the model and prediction as a file. If SVMBridge gets file pathes, it will not try to reread the written model nor the predictions. Sometimes you do not need the predictions, neither on memory nor on disk. In this case you can pass "/dev/null" as prediction file. This will make the SVM Test write to null, so it will not take any I/O time,  and therefore the SVMBridge will not reread the predictions, as it was already written on disk.
